Developing a preprint culture in biology

### 2012-09-28 ms.tex
revision of the intro

\keywords{Publishing; preprint server; arXiv; Green Open Access.}

@@

Public preprints servers allow authors to make their manuscripts publicly
available before, or in parallel to, submitting them to journals for traditional
peer-review. This idea gained popularity 20 years ago with the advent of arXiv,
an open preprint server widely used in physics and mathematics \cite{gin11}. 
It is also part of other fields' culture. Paul Krugman noted that, in economics,
the \emph{traditional model of submit, get refereed, publish, and then people
will read your work broke down a long time ago. In fact, it had more or less
fallen apart by the early 80s} \cite{kru12}. In addition to a section in arXiv,
economists have also the RePEc (Research Papers in Economics) initiative, which
aims to create an archive of working papers, manuscripts, and book chapters.

The idea behind preprint servers is fundamentally simple: to make the results
available to the scientific community as soon as possible rather than wait until
the peer-review process is fully completed. The point of arXiv and open
preprints servers is not to avoid the peer-review process. Almost all
manuscripts on arXiv are submitted to peer-review.  The point is that sharing
ideas as quickly as possible using preprint servers has numerous advantages.
These include rapid dissemination of work in progress to a wider audience, not
only scientists and the general public but also readers in developing countries
where access to subscription journals are often a limiting factor. Further,
preprints provide the opportunity to solicit feedback from a larger pool of
reviewers. As a consequence, preprint servers increase the number of
opportunities for review and revision prior to publication, resulting in higher
quality submissions which could also alleviate reviewer burden.

Yet, despite the success of the approach in other fields of inquiry, most
manuscripts in biology are never submitted to any public archive.  In this
article, we will first highlight the advantages of open preprints servers for
both scientists and publishers. We will also debunk a few misconceptions,
discuss the policies of major publishers in biology, and briefly review the most
popular open preprint servers.

>>>>

\keywords{Publishing; preprint server; Green Open Access; arXiv.}

@@

Public preprints servers allow authors to make their manuscripts publicly
available before, or in parallel to, submitting them to journals for traditional
peer-review. The idea behind preprint servers is fundamentally simple: to make
the results available to the scientific community as soon as possible rather
than wait until the peer-review process is fully completed. The point of arXiv
and open preprints servers is not to avoid the peer-review process. Almost all
manuscripts on arXiv are submitted to peer-review.  The point is that sharing
ideas as quickly as possible using preprint servers has numerous advantages.
These include rapid dissemination of work in progress to a wider audience, not
only scientists and the general public but also readers in developing countries
where access to subscription journals are often a limiting factor. Furthermore,
preprints provide the opportunity to solicit feedback from a larger pool of
reviewers and can be seen as an integral aspect of a vigorous peer-review
process \cite{hoc12}. Thus, preprint servers increase the number of
opportunities for review and revision prior to publication, resulting in higher
quality submissions which could also alleviate reviewer burden.

The idea gained popularity 20 years ago with the advent of arXiv, an open
preprint server widely used in physics and mathematics \cite{gin11}.  It is also
part of other fields' culture. Paul Krugman noted that, in economics, the
\emph{traditional model of submit, get refereed, publish, and then people will
read your work broke down a long time ago. In fact, it had more or less fallen
apart by the early 80s} \cite{kru12}. In addition to a section in arXiv,
economists have also the RePEc (Research Papers in Economics) initiative, which
aims to create an archive of working papers, manuscripts, and book chapters.
Yet, despite the success of the approach in other fields of inquiry, most
manuscripts in biology are never submitted to any public archive.  In this
article, we will first highlight the advantages of open preprints servers for
both scientists and publishers. We will also debunk a few misconceptions,
discuss the policies of major publishers in biology, and briefly review the most
popular open preprint servers.
